Revisiting Multi-Domain Machine Translation

### 2020-05-13 2020/coling2020/multidomain.tex

\newcite{Farajian17multidomain} does not use domain tags in training. The processing of each test sentence triggers the selection of a small set of related instances; using these, a generic NMT is tuned for some epochs, before delivering its output. This approach entirely dispenses with the notion of domain and relies on data selection techniques to handle data heterogeneity. \jcTodo{cite Xu et al 2019, Lexical Micro-adaptation for Neural Machine Translation}

>>>>

Finally, \newcite{Farajian17multidomain}, \newcite{li-etal-2018-one} and \newcite{xu2019} follow a different strategy. The processing of each test sentence triggers the selection of a small set of related instances; using these, a generic NMT is tuned for some iterations, before delivering its output. This approach entirely dispenses with the notion of domain and relies on data selection techniques to handle data heterogeneity.
